Implications of uniformly distributed, empirically informed priors for phylogeographical model selection: A reply to Hickerson et al.

### 2014-07-30 manuscripts/reply/reply-main.tex
More minor tweaks to intro of reply ms.

If support for models with few divergence events is caused by their larger
marginal likelihoods, we need to correct the model; improving the estimation
machinery will only increase our ability to estimate true posteriors that are
difficult to interpret.
Accordingly, \citet{Oaks2014dpp} has introduced a method that uses more
flexible probability distributions to accommodate prior uncertainty in
divergence times without overly inhibiting the marginal likelihoods of models
with more divergence-time parameters.
This greatly increases the method's robustness and power to detect temporal
variation in divergences \citep{Oaks2014dpp}.
This is not surprising given the rich statistical literature showing that
marginal likelihoods are very sensitive to the priors used in Bayesian model
selection
\citep[e.g.,][]{Jeffreys1939,Lindley1957}.

>>>>

If support for models with few divergence events is caused by their larger
marginal likelihoods, we need to correct the model; improving the estimation
machinery will only increase our ability to estimate misleading posteriors.
Accordingly, \citet{Oaks2014dpp} has introduced a method that uses more
flexible probability distributions to accommodate prior uncertainty in
divergence times without overly inhibiting the marginal likelihoods of models
with more divergence-time parameters.
This greatly increases the method's robustness and power to detect temporal
variation in divergences \citep{Oaks2014dpp}.
This is not surprising given the rich statistical literature showing that
marginal likelihoods are very sensitive to the priors used in Bayesian model
selection
\citep[e.g.,][]{Jeffreys1939,Lindley1957}.
